{\color {red}better title eventually}

### 2015-05-12 cs261n-paper/paper.tex
Spell check.

\subsection{Lessons Learned} 
\indent \indent During the pilot study, we were attempting to test out a comprehensive set of 
features for the Tor Browser. Our users had difficulties completing all the given tasks in the 
time alloted for the experiment. Additionally, user fatigue was very evident, with users not 
engaging in the later set of tasks after being tired from the download and install process. 
To ensure that the experiment does not cause user fatigue, we select a smaller set of features 
as the target for the full-scale study.  After deliberating with Tor developers, and testing out
various features on our own, we chose to focus on the Tor Browser connection configuration 
dialog because of its crucial role in censorship circumvention.

@@

Then, each participant will be given about 30 minutes to complete their given Internet browsing tasks. 
Note that these Internet tasks themselves do not take very much time, but that the time is alloted in order
for participants to complete the configuration process. We believe that this is more than enough time to 
test the usability of the configuration process. Even if some participants may have succeeded with more 
time, we consider these cases to be a failure from a usability perspective as this would require too much
time from a user in the wild. Minimal interaction will be allowed with participants and the researchers. 
Researchers may inform participants of specific information (such as a bridge address) in a manner 
which does not disturb other participants (such as instructing users to visit a specific non-blocked website 
containing this information).

@@

\subsection{Censorship Environment Simulation}
\indent \indent For our experiment, we plan to simulate and test three distinct censorship environments
which vary in their methods of censorship and thusly require distinct responses from our 
participants to circumvent successfully. These environments are designed with respect to 
common censorship techniques employed 
today along with knowledge of how pluggable transports will need to be used.
For instance, some of Tor's pluggable transports work in censorship environments
where others do not. Additionally, some of them require additional information (like bridge 
addresses) before they enable the user to successfully circumvent censorship. 
Details of the three censorship environments are below, increasing in 
order of censorship comprehensiveness and, therefore, difficulty to circumvent.

@@

We plan to solicit feedback on the design of this experiment at HotPETS2015.
Specifically, we would want a reliable way to target the testing of 
specific transports. But given that the average user would not have domain knowledge of 
what transports are for Tor, is there anything to infer from participants' selection of transports, 
or do we assume they are trying transports at random?

@@

We plant to solicit feedback on the design of this experiment at HotPETS2015. 
Circumvention is broader than the stereotypical ``dissident blogger'' 
use case. We will solicit feedback on which additional tasks will provide additional insight,
or if there are different tasks which are representative of other censorship evasion use cases.

@@

\section{Future Work}
\indent \indent With the high-level design of the experiment complete and IRB approval  to conduct this
experiment,  the next steps are to implement the simulated censorship environments which participants 
will be placed in and to write the browser extension which will collect the empirical data. 
We wait on these tasks in order to incorporate the feedback on the design of this experiment 
we will receive at HotPETS2015, which will take place during July. We plan to conduct this study starting 
August 2015.

@@

\noindent Specifically, the questions are as follows: 
\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
\item What session did you attend?  
\item What is your participant ID? (This can be found on the sticker on the left hand corder of desk you are currently sitting at.) 
\item What is your gender? 
\item What is your age? 
\item Please select your highest level of education. 
\item What is your current occupation?*
\item How familiar were you with Tor prior to this study? 
\item Were you confident that Tor was able to provide you with security and anonymity while completing your tasks?
\item Did anything unexpected happen while using Tor?*
\item What, if any, of the following could use improvement?*
\item Based on your experience, would you use Tor again?*
\item How many hours a week would you say you spend on the internet? 
\item How concerned are you about your privacy on the Internet?
\item How concerned are you about staying anonymous on the internet?
\item How concerned are you about being censored while you browse the Internet? 
\item How familiar are you with computer security? 
\item What kinds of computer security software do you use? 
\end{enumerate}

>>>>

\subsection{Lessons Learned} 
\indent \indent During the pilot study, we were attempting to test out a comprehensive set of 
features for the Tor Browser. Our users had difficulties completing all the given tasks in the 
time allotted for the experiment. Additionally, user fatigue was very evident, with users not 
engaging in the later set of tasks after being tired from the download and install process. 
To ensure that the experiment does not cause user fatigue, we select a smaller set of features 
as the target for the full-scale study.  After deliberating with Tor developers, and testing out
various features on our own, we chose to focus on the Tor Browser connection configuration 
dialog because of its crucial role in censorship circumvention.

@@

Then, each participant will be given about 30 minutes to complete their given Internet browsing tasks. 
Note that these Internet tasks themselves do not take very much time, but that the time is allotted in order
for participants to complete the configuration process. We believe that this is more than enough time to 
test the usability of the configuration process. Even if some participants may have succeeded with more 
time, we consider these cases to be a failure from a usability perspective as this would require too much
time from a user in the wild. Minimal interaction will be allowed with participants and the researchers. 
Researchers may inform participants of specific information (such as a bridge address) in a manner 
which does not disturb other participants (such as instructing users to visit a specific non-blocked website 
containing this information).

@@

\subsection{Censorship Environment Simulation}
\indent \indent For our experiment, we plan to simulate and test three distinct censorship environments
which vary in their methods of censorship and thus require distinct responses from our 
participants to circumvent successfully. These environments are designed with respect to 
common censorship techniques employed 
today along with knowledge of how pluggable transports will need to be used.
For instance, some of Tor's pluggable transports work in censorship environments
where others do not. Additionally, some of them require additional information (like bridge 
addresses) before they enable the user to successfully circumvent censorship. 
Details of the three censorship environments are below, increasing in 
order of censorship comprehensiveness and, therefore, difficulty to circumvent.

@@

We plan to solicit feedback on the design of this experiment at HotPETs 2015.
Specifically, we would want a reliable way to target the testing of 
specific transports. But given that the average user would not have domain knowledge of 
what transports are for Tor, is there anything to infer from participants' selection of transports, 
or do we assume they are trying transports at random?

@@

We plant to solicit feedback on the design of this experiment at HotPETs 2015. 
Circumvention is broader than the stereotypical ``dissident blogger'' 
use case. We will solicit feedback on which additional tasks will provide additional insight,
or if there are different tasks which are representative of other censorship evasion use cases.

@@

\section{Future Work}
\indent \indent With the high-level design of the experiment complete and IRB approval  to conduct this
experiment,  the next steps are to implement the simulated censorship environments which participants 
will be placed in and to write the browser extension which will collect the empirical data. 
We wait on these tasks in order to incorporate the feedback on the design of this experiment 
we will receive at HotPETs 2015, which will take place during July. We plan to conduct this study starting 
August 2015.

@@

\noindent Specifically, the questions are as follows: 
\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
\item What session did you attend?  
\item What is your participant ID? (This can be found on the sticker on the left hand corner of desk you are currently sitting at.) 
\item What is your gender? 
\item What is your age? 
\item Please select your highest level of education. 
\item What is your current occupation?*
\item How familiar were you with Tor prior to this study? 
\item Were you confident that Tor was able to provide you with security and anonymity while completing your tasks?
\item Did anything unexpected happen while using Tor?*
\item What, if any, of the following could use improvement?*
\item Based on your experience, would you use Tor again?*
\item How many hours a week would you say you spend on the internet? 
\item How concerned are you about your privacy on the Internet?
\item How concerned are you about staying anonymous on the internet?
\item How concerned are you about being censored while you browse the Internet? 
\item How familiar are you with computer security? 
\item What kinds of computer security software do you use? 
\end{enumerate}
